Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
halfway to adding Rust to the C++/Java table

% ---------------- C++ table UM Only--------------------------
\begin{table}[hbtp]
\centering
\caption{Regex vs. Comby for C++ (top) and Java (bottom)}
\label{tab:table_cpp1java}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule\toprule
\mc{6}{c}{\textbf{C++}} \\\midrule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
ompl & 525 & $\frac{595}{2533}$ & 23.49\% &  $\frac{564}{2127}$  & 25.94\%   \\[1ex]
libgraphqlparser& 137 & $\frac{157}{741}$ & 21.19\%  & $\frac{131}{440}$ & 29.77\% \\[1ex]
rethinkdb\_rebirth &471 &  $\frac{545}{2246}$ & 24.27\% & $\frac{492}{2009}$ & 24.49\% \\[1ex]
xoreos & 732  & $\frac{2419}{3876}$  & 62.41\% & $\frac{2280}{3297}$ & 69.15\% \\[1ex]
libxmljs &630 &  $\frac{881}{3989}$ & 22.09\% & $\frac{790}{4008}$ & 19.71\% \\[1ex]
tiny-diff.-simulator &  195 & $\frac{747}{1282}$ &58.27\% &$\frac{770}{1214}$ & 63.43\% \\[1ex]
\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrr}
                  & &       & Valid  & Invalid  & \% \\\midrule
 \multirow{4}{*}{\textbf{Overall}} & \multirow{2}{*}{Regex} & Mean     & 890.67 &  1553.83 & 35.28\% \\
%                          & & Med.    & 671.00 & 1579.00  & 23.88\%   \\
                          & & Std.Dev. & 787.62 & 956.31   & 19.48\%  \\\cline{2-6}
  & \multirow{2}{*}{Comby}  & Mean     & 837.83 & 1352.50 & 38.75\%  \\
%                         & & Med.    & 667.00 & 1267.00 & 27.86\%  \\
                         & & Std.Dev. & 745.78 & 1058.33& 21.66\%  \\\bottomrule
 \end{tabularx}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule
\mc{6}{c}{\textbf{Java}} \\\midrule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
 pebble         & 279 & $\frac{86}{1014}$ & 8.48\% & $\frac{85}{752}$ & 11.30\%  \\[1ex]
 spring-hateoas & 397 & $\frac{248}{2479}$ & 10.00\% & $\frac{172}{1384}$ & 12.43\%  \\[1ex]
 javacc         & 363 & $\frac{542}{1888}$ & 28.70\% & $\frac{494}{1281}$ & 38.71\%  \\[1ex]
 coffee-gb      & 463 & $\frac{224}{1927}$ & 11.63\% & $\frac{174}{798}$ & 21.80\% \\[1ex]
 egads          & 252 & $\frac{624}{2427}$ & 25.43\% & $\frac{597}{1163}$ & 51.33\%  \\[1ex]
 apk-parser     & 324 & $\frac{351}{1583}$ & 22.17\% & $\frac{333}{1199}$ & 27.77\%  \\[1ex]\midrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrr}
              & & & Valid  & Invalid  & \% \\\midrule
\multirow{4}{*}{\textbf{Overall}} & \mr{2}{Regex} & Mean     &  345.83 & 1545.00  & 17.74\% \\
%              &   & Med.     & 299.50 & 1524.50 & 16.90\%  \\
              &   & Std.Dev. & 203.86 & 467.98 & 8.73\%  \\\cline{2-6}
& \mr{2}{Comby} & Mean     & 309.17 & 786.17 & 27.22\% \\
%              &   & Med.     & 253.50 & 724.50 & 24.79\% \\
              &   & Std.Dev. & 202.44 & 235.24  & 15.59\% \\\bottomrule
\end{tabularx}
\end{table}

@@

\begin{table}[htbp]
\centering
\caption{C++ (Our Implementation vs. Dextool)}
\label{tab:table_cpp2}
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|r|r|r|r|}
\hline
 &  & \textbf{Killed} & \textbf{Not Killed} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{Equivalent \%} \\ \hline

 \multirow{3}{*}{\small ompl} & Regex & 29 & 566 & 0.05 & 30\% \\\cline{2-6}
    & Comby & 41 & 523 & 0.07 & 40\% \\\cline{2-6}
    & Dextool & 23 & 255 & 0.08 & N/A \\ \hline
\multirow{3}{*}{\small libgraphqlparser} & Regex & 142 & 15 & 0.90 & 30\% \\\cline{2-6}
    & Comby & 116 & 15 & 0.89 & 20\% \\ \cline{2-6}
    & Dextool & 50 & 2 & 0.96 & N/A \\ \hline
\multirow{3}{*}{\small rethinkdb\_rebirth} & Regex & 65 & 480 & 0.12 & 10\% \\\cline{2-6}
    & Comby & 49 & 443 & 0.10 & 20\% \\ \cline{2-6}
    & Dextool & 9 & 16 & 0.36 & N/A \\ \hline

\multirow{3}{*}{\small xoreos} & Regex & 33 & 2386 & 0.01 & 0\% \\\cline{2-6}
    & Comby & 33 & 2247 & 0.01 & 10\% \\ \cline{2-6}
    & Dextool & 8 & 406 & 0.02 & N/A \\ \hline
\multirow{3}{*}{\small libxmljs} & Regex & 547 & 334 & 0.62 & 10\% \\\cline{2-6}
    & Comby & 507 & 283 & 0.64 & 10\% \\ \cline{2-6}
    & Dextool & 383 & 447 & 0.46 & N/A \\ \hline
\multirow{3}{*}{\small tiny-differentiable-simulator} & Regex & 38 & 709 & 0.05 & 0\% \\\cline{2-6}
    & Comby & 32 & 738 & 0.04 & 0\% \\ \cline{2-6}
    & Dextool & 13 & 48 & 0.21 & N/A\\ \hline

\multirow{9}{*}{Overall} & \multirow{3}{*}{Regex} & \multicolumn{2}{c|}{Mean} & 0.29  & 13.33\%\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.09 & 10.00\% \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.38 & 13.66\% \\\cline{2-6}

 & \multirow{3}{*}{Comby} & \multicolumn{2}{c|}{Mean} & 0.29 & 16.67\% \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.09 & 15.00\% \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.37 & 13.66\% \\\cline{2-6}

 & \multirow{3}{*}{Dextool} & \multicolumn{2}{c|}{Mean} & 0.33 & N/A\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.29 & N/A \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.38 & N/A \\ \hline

>>>>

% ---------------- C++ table UM Only--------------------------
\begin{table}[hbtp]
\centering
\caption{Regex vs. Comby for C++ (top), Java (middle), and Rust (bottom)}
\label{tab:table_cpp1java}
\begin{tabularx}{\columnwidth}{X|r|rr|rr}
\toprule\toprule
\mc{6}{c}{\textbf{C++}} \\\midrule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & \textbf{Muts} & \textbf{\% Valid} & \textbf{Muts} &  \textbf{\% Valid} \\\midrule
ompl & 525 & 2533 & 23.49\% &  2127  & 25.94\%   \\
libgraphqlparser& 137 & 741 & 21.19\%  & 440 & 29.77\% \\
rethinkdb\_rebirth &471 & 2246 & 24.27\% & 2009 & 24.49\% \\
xoreos & 732  & 3876  & 62.41\% & 3297 & 69.15\% \\
libxmljs &630 &  3989 & 22.09\% & 4008 & 19.71\% \\[0.5ex]
tiny-diff.-simulator &  195 & 1282 &58.27\% & 1214 & 63.43\% \\
\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrr}
                  & &       & \textbf{Valid}  & \textbf{Invalid}  & \textbf{\% Valid} \\\midrule
 \multirow{4}{*}{\textbf{Overall}} & \multirow{2}{*}{\bf Regex} & Mean     & 890.67 &  1553.83 & 35.28\% \\
%                          & & Med.    & 671.00 & 1579.00  & 23.88\%   \\
                          & & Std.Dev. & 787.62 & 956.31   & 19.48\%  \\\cline{2-6}
  & \multirow{2}{*}{\bf Comby}  & Mean     & 837.83 & 1352.50 & 38.75\%  \\
%                         & & Med.    & 667.00 & 1267.00 & 27.86\%  \\
                         & & Std.Dev. & 745.78 & 1058.33& 21.66\%  \\\bottomrule
 \end{tabularx}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule
\mc{6}{c}{\textbf{Java}} \\\midrule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & \textbf{Mutants} & \textbf{\% Valid} & \textbf{Mutants} &  \textbf{\% Valid} \\\midrule
 pebble         & 279 & 1014 & 8.48\%  & 752 & 11.30\%  \\[1ex]
 spring-hateoas & 397 & 2479 & 10.00\% & 1384 & 12.43\%  \\[1ex]
 javacc         & 363 & 1888 & 28.70\% & 1281 & 38.71\%  \\[1ex]
 coffee-gb      & 463 & 1927 & 11.63\% & 798 & 21.80\% \\[1ex]
 egads          & 252 & 2427 & 25.43\% & 1163 & 51.33\%  \\[1ex]
 apk-parser     & 324 & 1583 & 22.17\% & 1199 & 27.77\%  \\[1ex]\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrr}
              & & & Valid  & Invalid  & \% \\\midrule
\multirow{4}{*}{\textbf{Overall}} & \mr{2}{Regex} & Mean     &  345.83 & 1545.00  & 17.74\% \\
%              &   & Med.     & 299.50 & 1524.50 & 16.90\%  \\
              &   & Std.Dev. & 203.86 & 467.98 & 8.73\%  \\\cline{2-6}
& \mr{2}{Comby} & Mean     & 309.17 & 786.17 & 27.22\% \\
%              &   & Med.     & 253.50 & 724.50 & 24.79\% \\
              &   & Std.Dev. & 202.44 & 235.24  & 15.59\% \\\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule
\mc{6}{c}{\textbf{Rust}} \\ \midrule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
cargo release    & 346          & $\frac{851}{2014}$   & 42.25\%  & $\frac{1690}{2401}$   & 70.39\% \\[1ex]
passarine        & 376          & $\frac{213}{2294}$   & 9.29\%  & $\frac{173}{1691}$   & 10.23\% \\[1ex]
typos            & 463          & $\frac{386}{1920}$   & 20.10\%  & $\frac{366}{1565}$   & 23.39\% \\[1ex]
ord              & 533          & $\frac{762}{2858}$   & 26.66\%  & $\frac{643}{2312}$   & 27.81\% \\[1ex]
bazuka           & 285          & $\frac{451}{1554}$   & 29.02\%  & $\frac{402}{1322}$   & 30.41\% \\[1ex]
strum            & 90           & $\frac{51}{428}$     & 11.92\%  & $\frac{50}{368}$     & 13.58\% \\[1ex]\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrr}
               & & & Valid  & Invalid  & \% \\\midrule
 \multirow{6}{*}{\textbf{Overall}} & \mr{3}{Regex} & Mean     &  452.33 &  1392.33 & 23.21\% \\
               &   & Std.Dev. & 309.05 & 656.76 & 12.16\%  \\\cline{2-6}
 & \mr{3}{Comby} & Mean     & 554.00 &  1055.83 & 29.29\% \\
 %              &   & Med.     & 253.50 & 724.50 & 24.79\% \\
               &   & Std.Dev. & 592.63 & 508.30 & 21.63\%  \\\bottomrule
\end{tabularx}}

@@
